Medical Concept Extraction

### 2012-12-14 paper/paper.tex
Progress on the system section.

Include a system diagram of the code base.

All of the code is available online at the following url:

@@

\subsubsection{Commandline Utilities}

@@

>>>>

\begin{figure}
\begin{center}
	\includegraphics[width=1\columnwidth]{figures/system.png}
\end{center}
\caption{An overview of the system and codebase.}
\label{fig:system}
\end{figure}

We built a fairly comprehensive framework for applying machine learning techniques to NLP domains. We built out a series of useful and reusable library modules and command line utilities to perform various tasks. An overview of the codebase can be seen in Figure~\ref{fig:system} and  all of the code is available online at the following url:

@@

\subsubsection{Data Formats and File I/O}

\subsubsection{Feature Computation}

\subsubsection{Model Encapsulation and Serialization}

\subsubsection{Learning Algorithms}

\subsubsection{Data Organization \& Directory Structure}

\subsubsection{Command-line Utilities}

@@

Training time
